Functional Pearl \\ Programming with Negative and Fractional Types

### 2012-02-19 dual.tex
small change

@@

>>>>

It is critical that the framework in which the negative types are introduced
is a framework in which all information is preserved, with no duplication or
erasure. This guarantees that the generated debts are paid once and exactly
once.

@@

Again it is critical that the framework in which the fractional types are
introduced is a framework in which all information is preserved, with no
duplication or erasure. This guarantees that the generated constraints are
satisfied once and exactly once.
